---
title: "Get RNA Arrays annotation data from Bioconductor"
output: html_document
---

###I want to get for example the gene symbols for each probe in a given array.


I will use the [MOE430A](https://bioconductor.org/packages/release/data/annotation/html/moe430a.db.html) and [MOE430B](https://bioconductor.org/packages/release/data/annotation/html/moe430b.db.html) chip annotations from bioconductor.


You can get them using the following code, after uncommenting:

```{r}
#source("https://bioconductor.org/biocLite.R")
#biocLite("moe430a.db")
#biocLite("moe430b.db")
```

Now we load the libraries and get the data

```{r, message = FALSE, warning=FALSE}
library(moe430a.db)
library(moe430b.db)
library(dplyr)
```

According to the [documentation](https://bioconductor.org/packages/release/data/annotation/manuals/moe430a.db/man/moe430a.db.pdf) we need to do the following:

```{r}
mapped_probes_a.keys <- mappedkeys(moe430aREFSEQ)
mapped_probes_a.df   <- as.data.frame(moe430aREFSEQ[mapped_probes_a.keys])
mapped_probes_b.keys <- mappedkeys(moe430bREFSEQ)
mapped_probes_b.df   <- as.data.frame(moe430bREFSEQ[mapped_probes_b.keys])
mapped_probes.df     <- unique(bind_rows(mapped_probes_a.df, mapped_probes_b.df))
rm(mapped_probes_a.keys, mapped_probes_b.keys, mapped_probes_a.df, mapped_probes_b.df)
```

The data is in the mapped_probes.df dataframe

```{r, echo=FALSE}
head(mapped_probes.df, n=10)
```

May be we would like to save the data frame in a .csv file

```{r}
write.csv(mapped_probes.df, "mapped_probes_df.csv")
```

So that we can open it later

```{r}
again_mapped_probes.df <- read.csv("mapped_probes_df.csv")
```

###Done!

