---
title: "Get transcripts data from Bioconductor"
output: html_document
---

###In this example, I will extract the 3'UTR length from all mouse RefSeq transcripts

I will use the [GenomicRanges](https://bioconductor.org/packages/release/bioc/html/GenomicRanges.html) library from Bioconductor to extract the 3'UTRs information.
Also, I will use the [dplyr](https://cran.rstudio.com/web/packages/dplyr/vignettes/introduction.html) library to handle the data.

```{r, message=FALSE, warning=FALSE}
library(GenomicFeatures)
library(dplyr)
```

Now, we need to load the data.

```{r}
#refSeq             <- makeTxDbFromUCSC(genom="mm10",tablename="refGene")
```

Since the function does not work at the moment (apparently something was changed in UCSC table),
I will load the data from a file. You download the data for the example by clicking [here](https://github.com/marcosmorgan/transcripts/raw/master/mm10_refseq.sqlite).

```{r}
refseq             <- loadDb("mm10_refseq.sqlite")
```

Now we get the 3'UTRs

```{r, warning=FALSE}
threeUTRs          <- threeUTRsByTranscript(refseq, use.names=TRUE)
length_threeUTRs   <- width(ranges(threeUTRs))
```

We put it all together in a dataframe

```{r}
the_lengths        <- as.data.frame(length_threeUTRs)
the_lengths        <- the_lengths %>% group_by(group, group_name) %>% summarise(sum(value))
the_lengths        <- unique(the_lengths[,c("group_name", "sum(value)")])
colnames(the_lengths) <- c("RefSeq Transcript", "3' UTR Length")
```

The data is in the the_lengths data frame

```{r, echo=FALSE}
head(the_lengths, n=10)
```

We can save the data for later

```{r}
write.csv(the_lengths, "the_lengths.csv")
```

And we can get it back

```{r}
again <- read.csv("the_lengths.csv")
```

###Done!







